|

### 2024-05-28 manuscript/paper.Rmd
Updated Manuscript.

@@

```{r echo = FALSE}
library(tidyverse)
library(ROCR)
model_list <- list()
#Indicate which model was used for each trai
model_list[["cle"]] <- 3
model_list[["ds1"]] <- 3
model_list[["ds2"]] <- 1
model_list[["ds3"]] <- 1
model_list[["ect"]] <- 1
model_list[["lps"]] <- 3
model_list[["lpt"]] <- 2
model_list[["maf"]] <- 1
model_list[["mav"]] <- 2
model_list[["mcv"]] <- 0
model_list[["mdf"]] <- 1
#model_list[["mds"]] <- 3
#model_list[["mpt"]] <- 0
model_list[["pmx"]] <- 3
model_list[["stl"]] <- 2
#model_list[["tpg"]] <- 1
library(here)
samps_stl <- readRDS(here("Figures/stl","posterior_samples_stl_2.RDS"))
mu_stl <- samps_stl %>% select(contains("mu"))
 maxtime <- 18
 results_prob_mu_diff_gt_mu_diff0 <- results_prob_mu_diff_gt_0 <- results_auc_mu_diff <-  data.frame()
for (phenotype in names(model_list)){
  samps <- readRDS(here(paste0("Figures/",phenotype),paste0("posterior_samples_",phenotype,"_",model_list[[phenotype]],".RDS")))
  gamma <- samps %>% select(gamma)
  mu <- samps %>% select(contains("mu"))
  if (phenotype == "stl") {
    mu_f <-
      mu[, 1:maxtime]
    mu_m <-
      mu[, (maxtime + 1):(2 * maxtime)]
  } else {

@@

@@

```{r auc-table, echo = FALSE, tab.cap= "AUC comparing time x versus time 0. \\label{auc-table}"}
results_auc_mu_diff_table <- results_auc_mu_diff %>%  mutate(auc_mu_diff = round(auc_mu_diff,3)) %>% pivot_wider(names_from = "phenotype", values_from = "auc_mu_diff")
#library(xtable)
xtable(results_auc_mu_diff_table[1,])
#knitr::kable(results_auc_mu_diff_table, caption = "The mtcars data.")
```

```{r prob0-plot, echo = FALSE, fig.cap = "Posterior probabilities that mean for males is greater than mean for females"}
ggplot(aes(x = time, y = prob_mu_diff_gt_0), data = results_prob_mu_diff_gt_0) + facet_wrap(~phenotype) + geom_path() + geom_hline(yintercept = 0.5, lty = 3) + ylim(0,1) + ylab("Posterior Probability")
```

>>>>

Figure \ref{fig:mu-diff-plot} shows the posterior mean difference for males versus females (values above 0 indicate means that were greater for males versus females).  The full poosterior distributions over time for all traits are shown in the appendix.

@@

```{r echo = FALSE}
library(tidyverse)
library(ROCR)
model_list <- list()
#Indicate which model was used for each trai
model_list[["cle"]] <- 3
model_list[["ds1"]] <- 3
model_list[["ds2"]] <- 1
model_list[["ds3"]] <- 1
model_list[["ect"]] <- 1
model_list[["lps"]] <- 3
model_list[["lpt"]] <- 2
model_list[["maf"]] <- 1
model_list[["mav"]] <- 2
model_list[["mcv"]] <- 0
model_list[["mdf"]] <- 1
#model_list[["mds"]] <- 3
#model_list[["mpt"]] <- 0
model_list[["pmx"]] <- 3
model_list[["stl"]] <- 2
#model_list[["tpg"]] <- 1
library(here)
samps_stl <- readRDS(here("Figures/stl","posterior_samples_stl_2.RDS"))
mu_stl <- samps_stl %>% select(contains("mu"))
 maxtime <- 18
 results_posterior_mean_diff <- results_prob_mu_diff_gt_mu_diff0 <- results_prob_mu_diff_gt_0 <- results_auc_mu_diff <-  data.frame()

for (phenotype in names(model_list)){
  samps <- readRDS(here(paste0("Figures/",phenotype),paste0("posterior_samples_",phenotype,"_",model_list[[phenotype]],".RDS")))
  gamma <- samps %>% select(gamma)
  mu <- samps %>% select(contains("mu"))
  if (phenotype == "stl") {
    mu_f <-
      mu[, 1:maxtime]
    mu_m <-
      mu[, (maxtime + 1):(2 * maxtime)]
  } else {

@@

  results_posterior_mean_diff <- rbind( results_posterior_mean_diff,data.frame(
    phenotype = phenotype,
    time = 1:18,
    mu_diff = apply(mu_diff,2,mean)
  ))

@@

```{r auc-table, echo = FALSE, tab.cap= "AUC comparing time x versus time 0. \\label{auc-table}"}
results_auc_mu_diff_table <- results_auc_mu_diff %>%  mutate(auc_mu_diff = round(auc_mu_diff,3)) %>% pivot_wider(names_from = "phenotype", values_from = "auc_mu_diff")
#library(xtable)
xtable(results_auc_mu_diff_table)
#knitr::kable(results_auc_mu_diff_table, caption = "The mtcars data.")
```

```{r mu-diff-plot, echo = FALSE, fig.cap = "Posterior mean difference between males and females"}
ggplot(aes(x = time, y = mu_diff), data = results_posterior_mean_diff) + facet_wrap(~phenotype, scale = "free_y") + geom_path() + geom_hline(yintercept = 0, lty = 3) + ylab("Posterior Mean")
```

```{r prob0-plot, echo = FALSE, fig.cap = "Posterior probabilities that mean for males is greater than mean for females"}
ggplot(aes(x = time, y = prob_mu_diff_gt_0), data = results_prob_mu_diff_gt_0) + facet_wrap(~phenotype) + geom_path() + geom_hline(yintercept = 0, lty = 3) + ylim(0,1) + ylab("Posterior Probability")
```
